# Example Senarios 

The goal of this code will be to introduce some easy ways to make your data tidy, perform efficient statistics, and visualize the results. 


### Things to Keep in Mind

+ Distributions (e.g., individual data points)
+ Minimize color 
+ Contrasting colors (Use prebuilt color palettes: Rcolorbrewer)
+ Minimize shape differences 
+ Text size (defaults are usually too small)
+ Show stats in the plot ideally
+ Keep in mind the medium (e.g., presentation, paper, poster)
+ Consistency 
+ Hot take: always code plots (for the most part)

### To Begin 

```{r, warning=FALSE, message=FALSE}
# load in necessary packages 
library(readr)
library(rstatix)
library(tidyverse)
library(ggpubr)
library(dplyr)
library(ggplot2)
library(cowplot)
```

```{r, warning=FALSE, message=FALSE}
# read in data 
PracticeData <- read_csv("Data/PracticeData.csv")
```

A few things of note about this data: 

+ There are three cohorts 
  + A: ART naive 
  + B: ART experienced
  + C: Healthy controls 
  
+ There are 2 visits
  + 2: 0 weeks 
  + 3: 24 weeks

+ There are 6 categories of BMI 
  + Severe_thinness
  + Moderate_thinnes
  + Mild_thinness
  + Normal
  + Overweight
  + Obese
  
+ There are 6 immune markers 
  + CD4+_count
  + CD4_PD1_Percent
  + CD4_CD103_Percent
  + CD4_HLADRpos_CD38pos_Percent
  + CRP_mg_L
  + Cortisol_ug_dL
  
### Potential Analyses 

What if we want to know significant differences in immune markers between cohorts stratifying by Visit? 

```{r, warning=FALSE, message=FALSE}
# make list of immune markers except CD4 count for now 
immune_markers <- c("CD4_PD1_Percent", "CD4_CD103_Percent",
                    "CD4_HLADRpos_CD38pos_Percent", "CRP_mg_L", "Cortisol_ug_dL")

# make data tidy 
tidy_data <- PracticeData %>% 
  select(Cohort_Short, Visit, all_of(immune_markers)) %>% 
  gather(-Cohort_Short, -Visit, 
         key = immune_cell, value = quantity)

# using rstatix we perform kruskall wallis tests with a Dunn's post hoc 
dunns_data <- tidy_data %>% 
  group_by(immune_cell, Visit) %>% 
  dunn_test(quantity~Cohort_Short) %>% 
  adjust_pvalue(method = 'bonferroni')

# plotting all results stratifying by visit 
dunns_data <- dunns_data %>% 
  add_xy_position(x = "Cohort_Short")

bxp <- ggplot(tidy_data, aes(x = Cohort_Short, y = quantity)) + 
          geom_boxplot() + 
          theme_bw() + 
          facet_grid(Visit~immune_cell) + 
          xlab("Cohort") + 
          ylab("")

bxp + 
  stat_pvalue_manual(dunns_data, label = "p.adj.signif")
```
  
For more statistical tests that rstatix can perform go to: https://rpkgs.datanovia.com/rstatix/
  


What if we want to combine multiple plots? 

```{r, warning=FALSE, message=FALSE}
# lets save previous boxplot 
sub_dunns <- dunns_data %>% 
  filter(immune_cell == "CD4_PD1_Percent" | immune_cell == "CD4_HLADRpos_CD38pos_Percent") %>% 
  mutate(Visit = case_when(Visit == 2 ~ 'Week 0', 
                           Visit == 3 ~ 'Week 24'))
fig1 <- tidy_data %>% 
  filter(immune_cell == "CD4_PD1_Percent" | immune_cell == "CD4_HLADRpos_CD38pos_Percent") %>% 
  mutate(Visit = case_when(Visit == 2 ~ 'Week 0', 
                           Visit == 3 ~ 'Week 24')) %>% 
  ggplot(aes(x = Cohort_Short, y = quantity)) + 
          geom_boxplot() + 
          theme_bw() + 
          facet_grid(Visit~immune_cell) + 
          ylim(0, 110) + 
          xlab("Cohort") + 
          ylab("") + 
          stat_pvalue_manual(sub_dunns, label = "p.adj.signif")

# quant by quant plot: immune activation by immune exhaustion
fig2 <- ggplot(PracticeData, aes(x = CD4_HLADRpos_CD38pos_Percent, y = CD4_PD1_Percent)) + 
          geom_point() + 
          geom_smooth(method = lm, ) + 
          stat_cor(label.x = 20, label.y = 85) + 
          theme_bw()

# lets see number of males and females by water source  
fig3 <- ggplot(PracticeData, aes(x = Main_Source_Water)) + 
          geom_bar(aes(fill = Gender)) + 
          theme_bw()




# Merge all plots using cowplot function plot_grid()
bottom_row <- plot_grid(fig2, fig3,
                  labels = c("B", "C"), 
                  ncol = 2, 
                  nrow = 1, 
                  hjust = -1, 
                  vjust = 0)

plot_grid(fig1, bottom_row, 
          labels = c("A", " "), 
          ncol = 1,
          nrow = 2, 
          rel_heights = c(1, 0.6),
          scale = 0.9, 
          hjust = -3)
```