Please run this first chunk so we all have a consistent database name and set of packages to start with. 

```{r, warning=FALSE, message=FALSE}
library(readr)
library(dplyr)
library(tidyverse)
library(rstatix) 
library(ggplot2)
library(ggpubr)
library(cowplot)

PracticeData <- read_csv("Data/PracticeData.csv")
```

If you want to add more packages you are more than welcome to do so in your respective code chunks.

## Group A 

For these two exercises please keep the old bad version and put it in a side by side comparison with your new and improved version. Think about the data that you have, what would be informative to an audience, be as creative as you want. 

### Excercise 1

Take this figure and improve it for a presentation. 

```{r, warning=FALSE, message=FALSE, out.width="100%"}
OG <- ggplot(PracticeData, aes(x = Main_Source_Water, y = Visit_Age)) + 
  geom_boxplot(aes(fill = BMI_Cat))

# first I want to reorder BMI categories so they reflect BMI from thin to obese
PracticeData$BMI_Cat <- ordered(PracticeData$BMI_Cat, levels = c("Severe_thinness", "Moderate_thinness", "Mild_thinness", "Normal", "Overweight", "Obese"))

# fix the plot a bit, basic stuff 
new_plot <- PracticeData %>% 
              mutate(Main_Source_Water = case_when(Main_Source_Water == 'a. Tap' ~ 'Tap',
                                                  Main_Source_Water == 'b. Bore hole' ~ 'Bore\nHole',
                                                  Main_Source_Water == 'c. Well' ~ 'Well')) %>% 
              ggplot(aes(x = Main_Source_Water, y = Visit_Age)) + 
                          geom_boxplot() + 
                          theme_bw() + 
                          ylab("Age") + 
                          xlab("Water Source") + 
                          labs(fill = "BMI Categories") + 
                          theme(text = element_text(size = 16)) + # change angle of x axis tick labels 
                          facet_wrap(~BMI_Cat)

# Extra idea 
# create a summary table and turn it into a heat map 
summary_table <- as.data.frame(table(PracticeData$Main_Source_Water, PracticeData$BMI_Cat))
colnames(summary_table) <- c("WaterSource", "BMICat", "Count") 

summary_heatmap <- summary_table %>% 
                      mutate(WaterSource = case_when(WaterSource == 'a. Tap' ~ 'Tap',
                                             WaterSource == 'b. Bore hole' ~ 'Bore\nHole',
                                             WaterSource == 'c. Well' ~ 'Well')) %>% 
                      ggplot(aes(x = WaterSource, y = BMICat, fill = Count)) + 
                                        geom_tile(show.legend = F) + 
                                        geom_text(aes(label = Count)) + 
                                        theme_bw() + 
                                        scale_fill_gradient(low = "white", high = "#1b98e0") + 
                                        xlab("Water Source") + 
                                        ylab("BMI Categories") + 
                                        theme(text = element_text(size = 16))

# This might be my solution 
plot_grid(new_plot, summary_heatmap, 
         ncol = 1, 
         nrow = 2, 
         rel_heights = c(1, 0.5))

# This is comparing the old and new plots 
plot_grid(OG, new_plot, 
          ncol = 2, 
          nrow = 1)
```

### Excercise 2

Take this figure and improve it for a publication.  

```{r, warning=FALSE, message=FALSE, out.width="100%"}
OG <- ggplot(PracticeData, aes(x=CRP_mg_L, y = BMI)) + 
        geom_point()

new_plot <- ggplot(PracticeData, aes(x=CRP_mg_L, y = BMI, color = Main_Source_Water)) + 
                geom_point() + 
                geom_smooth(method = "lm", se = F) +
                stat_cor() + 
                theme_bw() + 
                theme(text = element_text(size = 12)) + 
                xlab("CRP (mg/L)") +
                labs(color = "Water Source")  
  
plot_grid(OG, new_plot, 
          ncol = 2, 
          nrow = 1, 
          rel_widths = c(0.6,1))
```

## Group B 

Use colors in these plots, but please use a pre-built color palettes. 

### Excercise 3

Please view CD4 count differences between the difference cohorts and time points. 

Hint: first present at this column and determine what variable type it is. 

### Excercise 3

```{r, warning=FALSE, message=FALSE}
# get a palette 
library(RColorBrewer)
cohortColors <- palette(brewer.pal(n = 5, name = "PiYG"))

# remove cohort C and make prettier variables 
Cohorts_AB <- PracticeData %>% 
  filter(Cohort_Short != "C") %>% 
  mutate(Visit = case_when(Visit == 2 ~ "Week 0", 
                           Visit == 3 ~ "Week 24"), 
         Cohort_Short = case_when(Cohort_Short == "A" ~ "ART naive", 
                                  Cohort_Short == "B" ~ "ART exp"))
# make CD4 count numeric 
Cohorts_AB$`CD4+_count` <- as.numeric(Cohorts_AB$`CD4+_count`)
  
# R really doesnt like characters in column names so for downstream purposes 
# replace column name
colnames(Cohorts_AB)[colnames(Cohorts_AB) == 'CD4+_count'] <- 'CD4_count'

# perform statistical test 
krusk_test <- Cohorts_AB %>% 
  group_by(Visit) %>% 
  kruskal_test(CD4_count~Cohort_Short) %>% 
  mutate(group1 = "ART naive", # this is a hack 
         group2 = "ART exp") %>% 
  add_xy_position(x = "Cohort_Short")

# plot 
ggplot(Cohorts_AB, aes(x = Cohort_Short, y = CD4_count)) + 
  geom_boxplot(aes(fill = Cohort_Short), show.legend = F) + 
  scale_fill_manual(values = c(cohortColors[1], 
                               cohortColors[5])) + 
  theme_bw() + 
  theme(text = element_text(size = 12)) + 
  xlab("Cohort") + 
  ylab("CD4+ Count") + 
  facet_wrap(~Visit) + 
  stat_pvalue_manual(krusk_test, label = "p")
```

### Excercise 4

Illustrate differences in water source among men and women in the different cohorts. 

```{r, warning=FALSE, message=FALSE}
# get color palette
pal <- palette(brewer.pal(n = 2, name = "BrBG"))

# make data tidy 
sub <- PracticeData %>% 
  mutate(Cohort_Short = case_when(Cohort_Short == "A" ~ "ART naive", 
                           Cohort_Short == "B" ~ "ART exp", 
                           Cohort_Short == "C" ~ "HC")) %>% 
  group_by(Cohort_Short, Main_Source_Water) %>%
  count(Gender)

ggplot(sub, aes(x = Main_Source_Water, y = Gender, fill = n)) + 
  geom_tile(show.legend = F) +
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = pal[1], high = pal[3]) + 
  theme_bw() +
  facet_wrap(~Cohort_Short) + 
  xlab("Water Source") 
```

## Group C 

### Excercise 5

```{r, warning=FALSE, message=FALSE}

```

### Excercise 6

```{r, warning=FALSE, message=FALSE}

```

