Please run this first chunk so we all have a consistent database name and set of packages to start with. 

```{r, warning=FALSE, message=FALSE}
library(readr)
library(dplyr)
library(tidyverse)
library(rstatix) 
library(ggplot2)
library(ggpubr)
library(cowplot)

PracticeData <- read_csv("Data/PracticeData.csv")
```

If you want to add more packages you are more than welcome to do so in your respective code chunks.

## Group A 

For these two exercises please keep the old bad version and put it in a side by side comparison with your new and improved version. Think about the data that you have, what would be informative to an audience, be as creative as you want. 

### Excercise 1

Take this figure and improve it for a presentation. 

```{r, warning=FALSE, message=FALSE}
ggplot(PracticeData, aes(x = Main_Source_Water, y = Visit_Age)) + 
  geom_boxplot(aes(fill = BMI_Cat))
```

### Excercise 2

Take this figure and improve it for a publication.  

```{r, warning=FALSE, message=FALSE}
ggplot(PracticeData, aes(x=CRP_mg_L, y = BMI)) + 
  geom_point()
```

## Group B 

Use colors in these plots, but please use a pre-built color palettes. 

### Excercise 3

Please present CD4 count differences between the difference cohorts and time points. 

Hint: first look at this column and determine what variable type it is. 

```{r, warning=FALSE, message=FALSE}

```

### Excercise 4

Illustrate differences in water source among men and women in the different cohorts. 

```{r, warning=FALSE, message=FALSE}

```

## Group C 

These two problems are extremely similar, for extra credit you can try to add color to provide information on the directionality of the trend between groups or on p-value. 

### Excercise 5

Make all inter-cohort comparisons for all immune markers (not including CD4 counts), plot statistical significance

```{r, warning=FALSE, message=FALSE}

```

### Excercise 6

Make all intra-cohort comparisons for all immune markers (not including CD4 counts), plot statistical significance.

```{r, warning=FALSE, message=FALSE}

```